Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-26 paper.qmd
Added removed S-curve codes to another script

```{r}
#| label: scurve-training
training_data_scurve <- read_rds("data/s_curve/s_curve_training.rds")
```

<!--UMAP applied for Scurve data-->
```{r}
#| label: umap-scurve
umap_scurve <- read_rds(file = "data/s_curve/s_curve_umap.rds")

scurve_scaled_obj <- gen_scaled_data(
  data = umap_scurve)

umap_scurve_scaled <- scurve_scaled_obj$scaled_nldr
lim1 <- scurve_scaled_obj$lim1
lim2 <- scurve_scaled_obj$lim2
r2 <- diff(lim2)/diff(lim1)

>>>>

```{r}
#| label: two-curvy-training
training_data_two_curvy <- read_rds("data/two_curvy_clust/two_curvy_clust_data.rds")
```

<!--UMAP applied for Two curvy data-->
```{r}
#| label: umap-two-curvy
umap_two_curvy <- read_rds(file = "data/two_curvy_clust/two_curvy_clust_umap_n-neigbors_15_min-dist_0.1.rds")

two_curvy_scaled_obj <- gen_scaled_data(
  data = umap_two_curvy)

umap_two_curvy_scaled <- two_curvy_scaled_obj$scaled_nldr
lim1 <- two_curvy_scaled_obj$lim1
lim2 <- two_curvy_scaled_obj$lim2
r2 <- diff(lim2)/diff(lim1)
